---
output: html_document
---

```{r, here-i-am}
here::i_am("DATA550_finalproject/report.Rmd")
```
## Introduction
In this analysis I am investigating the association between prenatal
particulate matter exposure and child psychopathology in the Drakenstein
Child Health Study, a birth cohort based in Cape Town South Africa
(N=500). We measured particulate matter 2.5 (PM2.5) concentrations
during the second trimester of pregnancy. Child psychopathology was
measured at 6.5 years of age using the Child Behavior Checklist (CBCL).
I utilized the total problems scale, in which larger scores means that
the child is exhibiting more behavioral problems. I ran an adjusted
linear regression model to quantify the association between prenatal
PM2.5 and child total problems score. I adjusted for ethnicity, maternal
socioeconomic status, and maternal age as potentially important
covariates and confounders.

Since I cannot upload the actual data due to data use agreements and
privacy concerns, I simulated a dataset with similar variables.


## Descriptive Analysis

### Table 1- Study Characteristics of the Drakenstein Child Health Study

```{r, table1}
readRDS(
  file =here::here("DATA550_finalproject/output/table_one.RDS") #! TO DO: add appropriate file path to read table 1
)
```

## Regression Analysis

### Figure 1- Beta and confidence intervals for model

```{r, figure1, warning=F}
readRDS(
  file=here::here("DATA550_finalproject/output/figure_one.RDS")
)


```
